Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2022-08-31 supplement.tex
Update filtering section

All analyses presented in this work focus on biallelic single nucleotide
polymorphisms within the 1000 Genomes Phase 3 strict mask.  For the
\texttt{moments-LD} analysis, we focused on intergenic regions because these
appear less affected by natural selection compared to both synonymous and
nonsynonymous variation \citep{Ragsdale2018-dd}, removing regions that fell
outside of the 1000 Genomes strict callability mask. To enable comparison with
Neanderthal DNA, we excluded regions for which the Vindija Neanderthal sample
had less than 100 contiguous base pairs.

>>>>

All analyses presented in this work focus on biallelic single nucleotide
polymorphisms within the 1000 Genomes Phase 3 strict mask
($L_{included}=2,064,554,803$bp). To enable comparison with Neanderthal DNA, we
excluded regions for which the Vindija Neanderthal sample had less than 100
contiguous base pairs with high quality variant calls
($L_{included}=1,519,643,507$bp). For the \texttt{moments-LD} analysis, we
further focused on intergenic regions because these appear less affected by
natural selection compared to both synonymous and nonsynonymous variation
\citep{Ragsdale2018-dd} ($L_{included}=637,639,065$bp).

The 290 individuals used in the \texttt{moments-LD} inference featured
18,461,915 polymorphic biallelic SNPs genome-wide in the callable regions with
Neanderthal alignment, of which 8,115,115 were in intergenic and thus
putatively neutral regions.
